Clinical advancement forecasting \thanks{\textit{\underline{Citation}}: \textbf{TBD}}

### 2024-04-11 paper/paper.tex
Add improved opportunity figure

\begin{figure}[H]
  \centering
  \captionsetup{width=.9\linewidth}
  \includegraphics[width=1\textwidth]{dataset_statistics.png}
  \caption{
    \textbf{Training and evaluation dataset summary statistics}.
  }
  \label{fig:dataset_statistics}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \captionsetup{width=.9\linewidth}
  \includegraphics[width=1\textwidth]{relative_risk_model_features.pdf}
  \caption{
    \textbf{Performance by algorithm, constraint type and feature grouping}.  
  }
  \label{fig:relative_risk_model_features}
\end{figure}

>>>>

\begin{figure}[H]
  \centering
  \captionsetup{width=.9\linewidth}
  \includegraphics[width=1\textwidth]{dataset_statistics.png}
  \caption{
    \textbf{Training and evaluation dataset summary statistics}.\\\hspace{\textwidth}
    \textbf{balance}: percentage of TD pairs that eventually advanced beyond phase 2 \\\hspace{\textwidth} 
    \textbf{min\_year}: earliest year in which a TD pair has first advanced to phase 2 \\\hspace{\textwidth} 
    \textbf{n\_targets}: number of unique targets \\\hspace{\textwidth} 
    \textbf{n\_diseases}: number of unique diseases \\\hspace{\textwidth} 
    \textbf{n\_pairs}: number of TD pairs (equal to number of records) \\\hspace{\textwidth} 
    \textbf{n\_pairs\_wev}: number of TD pairs with directly associated evidence (i.e. not just target or disease evidence).
  }
  \label{fig:dataset_statistics}
\end{figure}

@@
